Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
removed placeholders

%Traditionally, it has been a challenge to relate between a simple cognitive state (such as `looking at a triangle`) and the corresponding activity of the brain \cite{Pone0001394}. This correspondence may even vary from subject to subject, making the challenge even harder. Since the introduction of fMRI, researchers have been able to acquire detailed measurements of brain activity, allowing for machine learning methods to be applied for the detection of patterns in fMRI data.

- briefly build up to state of the art, mention methods we tried?
- state of the art: probably multivariate pattern analysis! (\cite{Haxby2012852})

In the rest of this paper, we will discuss a number of machine learning techniques and their ability to classify our test data. In section~\ref{sec:methods} we will discuss the setup of our experiments and the analysis performed on our data. After that, in sections~\ref{sec:results} and ~\ref{sec:discussion}, we will present the results from these experiments and discuss them. We conclude this paper with a discussion on possible improvements and suggest some additional experiments that could be done.

@@

@@

To reducde the dimensionality of the input, two different methods are used.
ROI mapping. 
So how do we cope with this problem? On common solution is to reduce $|\vec{x}|$ by only using voxels belonging to a specific region of interest (ROI). However, this requires us to known which regions are actually of interest \textit{a priori}.
- ROIs, means, stddev, skew, kurtosis?

>>>>

%In the rest of this paper, we will discuss a number of machine learning techniques and their ability to classify our test data. In section~\ref{sec:methods} we will discuss the setup of our experiments and the analysis performed on our data. After that, in sections~\ref{sec:results} and ~\ref{sec:discussion}, we will present the results from these experiments and discuss them. We conclude this paper with a discussion on possible improvements and suggest some additional experiments that could be done.

@@

\subsection{Preprocessing}

@@

To reducde the dimensionality of the input, two different methods are used.

ROI mapping.

Principal Component Analysis (PCA).

So how do we cope with this problem? On common solution is to reduce $|\vec{x}|$ by only using voxels belonging to a specific region of interest (ROI). However, this requires us to known which regions are actually of interest \textit{a priori}.
- ROIs, means, stddev, skew, kurtosis?

\subsection{Classifiers}
